Citation network analysis of urban modeling research

### 2019-06-05 paper.tex
Update on Overleaf.
.

@@

@@

check modularity = f(horizontal and vertical depth) : insight into the relevant number of initially requested papers

Sensitivity of 'width' of paper. Width=the amount of hits in google scholar we use

Sensitivity of the used key words

>>>>

% \cite{ramadier2004transdisciplinarity} transdisciplinarity in urban studies
% \cite{batty2019map} the digital twin - need of reflexivity, hence understanding modeling landscape is crucial

@@

% \cite{giatsidis2019rooted} new measures based on subgraph density for citation networks

@@

% check modularity = f(horizontal and vertical depth) : insight into the relevant number of initially requested papers ; Sensitivity of 'width' of paper. Width=the amount of hits in google scholar we use ; Sensitivity of the used key words => all in same analysis

Before being able to proceed to any thematically relevant network analysis, a sensitivity analysis of network properties as a function of construction parameters is necessary. More particularly, the results may be strongly dependent on the number of search results retained and on the requests used. This preliminary aims at checking this dependency and extract the most robust subnetwork possible for the rest of the analysis.
